An Empirical Analysis of C Preprocessor Use

### 2002-12-29 macros/papers/emp-use-2.tex
Small changes that bring our source closer to the published version.

        An alternative solution would convert macros whose bodies are
        statements into semicolonless statements (wrapped in {\tt do \verb|{|
        {\rm \ldots}\verb|; }| while (0)}, as noted above).  Invocations of
        such macros look more like function calls are are less error-prone.
        This solution requires notifying users of the change in the macro's
        interface and changing all existing macro uses.

@@

  %%Numbers: read them off tbl-subset-categories.tex
  %% 2.0%: read off caption of fig/cat-def-frequency.eps
  \captionsmall{Categorization of definitions for each macro name with more
    than one definition.
    For instance, for 869 macro names (28\% of multiply-defined macro
    names), all definitions fall into the expression category, and for 183
    macro names (6.0\% of multiply-defined macro names), all definitions
    are either expressions or constants.
    Rows less than 0.2\%, representing 5 or fewer macro names, are omitted.
    The rightmost column indicates the categorization of the macro name; 
    4.4\% of all multiply-defined macro names, and 2.0\% macro names
    overall, are are categorized as ``other''.
    This chart shows which different macro definition categories tend
    to occur together and assists in understanding the reasons for macro names
    whose multiple definitions cause them to be categorized as ``other''.}

@@

\textbf{Michael D. Ernst} will receive the Ph.D. in Computer Science and
Engineering from the University of Washington in June 2000.  He has
previously been a lecturer at Rice University and a researcher at Microsoft
Research.  He holds the S.B. and S.M. degrees from MIT.  Ernst's primary
technical interest is programmer productivity, encompassing software
engineering, program analysis, compilation, and programming language
design.  However, he has also published in artificial intelligence, theory,
and other areas of computer science.

>>>>

        An alternative solution would convert macros whose bodies are
        statements into semicolonless statements (wrapped in {\tt do \verb|{|
        {\rm \ldots}\verb|; }| while (0)}, as noted above).  Invocations of
        such macros look more like function calls and are less error-prone.
        This solution requires notifying users of the change in the macro's
        interface and changing all existing macro uses.

@@

  %%Numbers: read them off tbl-subset-categories.tex
  %% 2.0%: read off caption of fig/cat-def-frequency.eps
  \captionsmall{Categorization of definitions for each macro name with more
    than one definition.
    For instance, for 869 macro names (28\% of multiply-defined macro
    names), all definitions fall into the expression category, and for 183
    macro names (6.0\% of multiply-defined macro names), all definitions
    are either expressions or constants.
    Rows less than 0.2\%, representing 5 or fewer macro names, are omitted.
    The rightmost column indicates the categorization of the macro name; 
    4.4\% of all multiply-defined macro names, and 2.0\% macro names
    overall, are categorized as ``other''.
    This chart shows which different macro definition categories tend
    to occur together and assists in understanding the reasons for macro names
    whose multiple definitions cause them to be categorized as ``other''.}

@@

\textbf{Michael D. Ernst} will receive the Ph.D. in Computer Science and
Engineering from the University of Washington in June 2000.  He has
previously been a lecturer at Rice University and a researcher at Microsoft
Research.  He holds the S.B. and S.M. degrees from MIT\@.  Ernst's primary
technical interest is programmer productivity, encompassing software
engineering, program analysis, compilation, and programming language
design.  However, he has also published in artificial intelligence, theory,
and other areas of computer science.
